Turbulence in compact to giant H~II regions

### 2023-04-28 strucfunc_paper.tex
Another typo

\begin{figure}
\centering 
\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
\caption{
  Panels a--g: Histograms (blue) of the probability density function (PDF)
  of the \ha{} surface brightness of \hii{} regions in our sample.
  Smooth lines (orange) show fitted log-normal distributions.
  In order to suppress fluctuations on scales
  smaller than the correlation length,
  surface brightness maps were rebinned by averaging
  into pixels of size \(0.5 r_0\) before calculating the PDF.
  \startNEW
  Panel~h: RMS Mach number of three-dimensional
  velocity fluctuations (panel~h)
  as a function of the RMS fractional brightness fluctuation calculated from the PDFs.
  The gray shaded area shows the range of predicted values
  for the brightness fluctuations if they are entirely due to density
  fluctuations formed by driven turbulence with the observed Mach number.
  Panel~i: Ratio of plane-of-sky to line-of-sight velocity dispersions
  as a function of the
  RMS fractional brightness fluctuations calculated from the PDFs.
  The solid and dashed lines show the expected relationship for
  the toy models of Appendix~\ref{sec:appar-veloc-fluct}. 
  \stopNEW
}
\label{fig:brightness-pdfs}
\end{figure}

>>>>

\begin{figure}
\centering 
\includegraphics[width=\linewidth]{Figures/bright-hist-multi}
\caption{
  Panels a--g: Histograms (blue) of the probability density function (PDF)
  of the \ha{} surface brightness of \hii{} regions in our sample.
  Smooth lines (orange) show fitted log-normal distributions.
  In order to suppress fluctuations on scales
  smaller than the correlation length,
  surface brightness maps were rebinned by averaging
  into pixels of size \(0.5 r_0\) before calculating the PDF.
  \startNEW
  Panel~h: RMS Mach number of three-dimensional
  velocity fluctuations
  as a function of the RMS fractional brightness fluctuation calculated from the PDFs.
  The gray shaded area shows the range of predicted values
  for the brightness fluctuations if they are entirely due to density
  fluctuations formed by driven turbulence with the observed Mach number.
  Panel~i: Ratio of plane-of-sky to line-of-sight velocity dispersions
  as a function of the
  RMS fractional brightness fluctuations calculated from the PDFs.
  The solid and dashed lines show the expected relationship for
  the toy models of Appendix~\ref{sec:appar-veloc-fluct}. 
  \stopNEW
}
\label{fig:brightness-pdfs}
\end{figure}
